Feasibility of Harvesting Power To Run A Domestic Water Meter Using Streaming Cell Technology

### 2014-10-14 paper.tex
Removed test

    \section{Readily Attainable Streaming Cell Efficiency} \label{sect:streamingCell}
    \begin{figure}
        \begin{center}
        \includegraphics[width=\linewidth]{Photo_streamingPotential_Assembly_Step3.JPG}
        \end{center}
        \caption{One of our ten constructed streaming cells mounted in an acrylic holder. Copper wires have been epoxied into each side to provide a means of measuring the developed potential across the cell. The plastic shims are visible as the orange strips at each side of the cell.}
        \label{fig:cell}
    \end{figure}

@@

    Our estimation shows a monitoring and transmitting device would need about \SI{6.96}{\joule} per day to operate in ideal transmission conditions.
    If the transmitter were to require $100\times$ more energy to transmit, as an estimate of poor conditions, the energy requirements would jump to \SI{9.39}{\joule} per day.
    It is therefore estimated that an energy harvester would need to deliver approximately \SI{10}{\joule} of energy per day.

@@

    \section{Sizing of Streaming Cell Harvester}
    \label{sect:harvesterSize}
    We now estimate the physical size of a harvester capable of supplying the energy to run a wireless water meter.
    Auckland tap water has a sodium content of 2.1--26.0\thinspace mg/L.~\cite{WatercareNewZealand2012}
    This equates to a Debye length in the range 0.3--\SI{1.0}{\nano\metre} and therefore the optimum channel height between 0.6--\SI{2.1}{\nano\metre}.
    We envision a harvester made from stacked layers of glass, each layer forming a rectangular channel similar to those constructed earlier.

>>>>

    \section{Readily Attainable Streaming Cell Efficiency} \label{sect:streamingCell}
    \begin{figure}
        \begin{center}
        \includegraphics[width=\linewidth]{Photo_streamingPotential_Assembly_Step3.JPG}
        \end{center}
        \caption{One of ten constructed streaming cells mounted in an acrylic holder. Copper wires have been epoxied into each side to provide a means of measuring the developed potential across the cell. The plastic shims are visible as the orange strips at each side of the cell.}
        \label{fig:cell}
    \end{figure}

@@

    Our estimation shows a monitoring and transmitting device would need about \SI{6.96}{\joule} per day to operate in ideal transmission conditions.
    If the transmitter were to require a hundred times more energy to transmit, as an estimate of poor conditions, the energy requirements would jump to \SI{9.39}{\joule} per day.
    It is therefore estimated that an energy harvester would need to deliver approximately \SI{10}{\joule} of energy per day.

@@

    \section{Sizing of Streaming Cell Harvester}
    \label{sect:harvesterSize}
    We now estimate the physical size of a harvester capable of supplying the energy to run a wireless water meter.
    Auckland tap water has a sodium content of 2.1--\SI{26.0}{\milli\gram\per\litre}.~\cite{WatercareNewZealand2012}
    This equates to a Debye length in the range 0.3--\SI{1.0}{\nano\metre} and therefore the optimum channel height between 0.6--\SI{2.1}{\nano\metre}.
    We envision a harvester made from stacked layers of glass, each layer forming a rectangular channel similar to those constructed earlier.
